---
title: "Summary of Results"
output: pdf_document
header-includes:
  - \usepackage{float}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.pos = 'H',fig.height = 6.5)
library(tidyverse)
library(tsutils)
library(kableExtra)
res<-read_csv('all_results.csv')

res%>%
  mutate(DGP=paste(DGPDistribution,DGPStationary,sep = '_'))%>%
  mutate(BaseMethod=paste(BaseDependence,BaseDistribution,sep = '_'))%>%
  select(EvaluationPeriod,Method,EnergyScore,DGP,BaseMethod,BaseModel)->matrix


BaseMs<-unique(matrix$BaseMethod)

res<-read_csv('meanScore.csv')

```

In all cases four methods are used to generate base forecasts.  Either base forecasts are drawn from an independent distribution or non-independent distribution (all DGPs actually have dependence).  Also base forecasts are Gaussian or use bootstrapping (the DGPs may be Gaussian or non-Gaussian)

#Gaussian and Stationary DGP

The DGP has Gaussian residuals and all series are forced to be stationary.

## ARIMA model

```{r}
model<-'arima'
dgps<-'stationary'
dgpd<-'gaussian'
```

Recall that the true DGP is ARIMA

```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi tests is below


```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

## ETS model

```{r}
model<-'ets'
```

Recall that the true DGP is ARIMA so there is model misspecification here.



```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi test below

```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

#Non Gaussian and Stationary DGP

The DGP has non-Gaussian residuals and all series are forced to be stationary.

## ARIMA model

```{r}
model<-'arima'
dgps<-'stationary'
dgpd<-'nongaussian'
```

Recall that the true DGP is ARIMA

```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi tests is below


```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

## ETS model

```{r}
model<-'ets'
```

Recall that the true DGP is ARIMA so there is model misspecification here.



```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi test below

```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

#Gaussian and non-Stationary DGP

The DGP has Gaussian residuals and some series are non stationary.

## ARIMA model

```{r}
model<-'arima'
dgps<-'nonstationary'
dgpd<-'gaussian'
```

Recall that the true DGP is ARIMA

```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi tests is below


```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

## ETS model

```{r}
model<-'ets'
```

Recall that the true DGP is ARIMA so there is model misspecification here.



```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi test below

```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

#Non Gaussian and non Stationary DGP

The DGP has non-Gaussian residuals and some series are non-stationary.

## ARIMA model

```{r}
model<-'arima'
dgps<-'nonstationary'
dgpd<-'nongaussian'
```

Recall that the true DGP is ARIMA

```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi tests is below


```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage

## ETS model

```{r}
model<-'ets'
```

Recall that the true DGP is ARIMA so there is model misspecification here.



```{r}
res%>%
  filter(DGPStationary==dgps,
         DGPDistribution==dgpd,
         BaseModel==model)%>%
  select(-DGPStationary,
         -DGPDistribution,
         -BaseModel)%>%
  kable(digits = 4)%>%
  kable_styling(font_size = 5)

```

Summary of Nemenyi test below

```{r,fig.cap=paste('Results for',model,'modelling with a',dgpd,dgps,'DGP',sep=' ')}
par(mfrow=c(2,2))
    for (b in BaseMs){
      matrix%>%
        filter(BaseModel==model)%>%
        filter(DGP==paste(dgpd,dgps,sep='_'))%>%
        filter(BaseMethod==b)%>%
        select(-DGP,-BaseMethod)%>%
        pivot_wider(names_from = Method, values_from = EnergyScore)%>%
        select(-EvaluationPeriod)->dat
      datm<-as.matrix(dat)
      if(nrow(dat)!=0){
        nemenyi(datm,plottype = 'matrix',main=b)->nn
      }else{
        plot(0,0,'n',main=b)
      }
        
      
    }
```

\clearpage
